Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to collapse personality clusters into one variable for GLAD/EDGI prepan

```{r Collapse personality disorder clusters}

@@

#Check that it worked
head(dat.retro$personality_cluster_a_numeric, 10)
head(dat.retro$personality_cluster_b_numeric, 10)
head(dat.retro$personality_cluster_c_numeric, 10)
head(dat.retro$personality_disorder_numeric, 10)

@@

>>>>

```{r Collapse personality disorder clusters for prepan data}

GLAD.prepan <- GLAD.prepan %>% 
  mutate(personality_disorder_numeric =
           case_when(
             personality_cluster_a_numeric == 1 | personality_cluster_b_numeric == 1 | personality_cluster_c_numeric == 1 ~ 1,
             personality_cluster_a_numeric == 0 & personality_cluster_b_numeric == 0 & personality_cluster_c_numeric == 0 ~ 0
           ))

#Check that it worked
head(GLAD.prepan$personality_cluster_a_numeric, 15)
head(GLAD.prepan$personality_cluster_b_numeric, 15)
head(GLAD.prepan$personality_cluster_c_numeric, 15)
head(GLAD.prepan$personality_disorder_numeric, 15)

```{r Collapse personality disorder clusters for retro data}

@@

#Check that it worked
head(dat.retro$personality_cluster_a_numeric, 15)
head(dat.retro$personality_cluster_b_numeric, 15)
head(dat.retro$personality_cluster_c_numeric, 15)
head(dat.retro$personality_disorder_numeric, 15)

@@

```{r Get PD positive for GLAD/EDGI}

GLAD.prepan_PD_positive <- GLAD.prepan %>%
  select(personality) %>% 
  filter(psychotic_disorders_numeric == 1)
